Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
Sprinkling some new results in there

\begin{table}[H]
  \begin{center}
  \caption{Clone instance contents} \label{table:contents}
  \medskip
\begin{tabular}{|l|l|l|}
  \hline
  \textbf{Contents} & \textbf{\#} & \textbf{\%} \\ \hline
  Partial Method     & 18,791 & 57.37 \\ \hline
  Several Methods         & 8,514 & 25.99 \\ \hline
  Includes Constructor  & 1,213 & 3.70 \\ \hline
  Includes Field        & 1,487 & 4.54 \\ \hline
  Partial Constructor      & 1,078 & 3.29 \\ \hline
  Only Fields           & 888 & 2.71 \\ \hline
  Full Method           & 284 & 0.87 \\ \hline
  Includes Class Declaration  & 258 & 0.79 \\ \hline
  Other Categories    & 243 & 0.74 \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

We measured the amount of clones that can be refactored through method extraction (without additional transformations being required). Our results are displayed in Table \ref{table:refactorability}. In this table we use the following categories:
\begin{itemize}
    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements.
    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
\end{itemize}

\begin{table}[H]
  \begin{center}
  \caption{Refactorability through method extraction} \label{table:refactorability}
  \medskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{}         & \textbf{\#} & \textbf{\%} \\ \hline
Is not a partial method     & 4,806 & 38.49 \\ \hline
Complex control flow  & 3,158 & 25.29 \\ \hline
Spans part of a block   & 3,152 & 25.24 \\ \hline
Can be extracted & 1,371 & 10.98 \\ \hline
\end{tabular}
\end{center}
\end{table}

From Table \ref{table:refactorability}, we can see that approximately ten percent of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances). For the other clones, other techniques or transformations will be required. Looking into these techniques and transformations will be one of our next steps.

>>>>

\begin{table}[H]
  \begin{center}
  \caption{Clone instance contents} \label{table:contents}
  \medskip
\begin{tabular}{|l|l|l|}
  \hline
  \textbf{Contents} & \textbf{\#} & \textbf{\%} \\ \hline
  Partial Method     & 79,945 & 78.80 \\ \hline
  Several Methods         & 7,323 & 7.22 \\ \hline
  Partial Constructor      & 4,385 & 4.32 \\ \hline
  Full Method           & 3,868 & 3.81 \\ \hline
  Only Fields           & 3,039 & 3.00 \\ \hline
  Includes Constructor  & 1,522 & 1.50 \\ \hline
  Includes Field        & 616 & 0.61 \\ \hline
  Includes Class Declaration  & 376 & 0.37 \\ \hline
  Other Categories    & 376 & 0.37\\ \hline
\end{tabular}
\end{center}
\end{table}

@@

We measured the amount of clones that can be refactored through method extraction (without additional transformations being required). Our results are displayed in Table \ref{table:refactorability}. In this table we use the following categories:
\begin{itemize}
    \item \textbf{Can be extracted:} This clone is a fragment of code that can directly be extracted to a method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
    \item \textbf{Complex control flow:} This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans part of a block:} This clone spans a part of a statement.
    \item \textbf{Is not a partial method:} If the clone does not fall in the ``Partial method'' category of Table \ref{table:contents}, the ``extract method'' refactoring technique cannot be applied.
\end{itemize}

\begin{table}[H]
  \begin{center}
  \caption{Refactorability through method extraction} \label{table:refactorability}
  \medskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{}         & \textbf{\#} & \textbf{\%} \\ \hline
Can be extracted     & 13,553 & 38.22 \\ \hline
Spans part of a block  & 12,332 & 34.78 \\ \hline
Is not a partial method   & 8,074 & 22.77 \\ \hline
Complex control flow & 1,503 & 4.24 \\ \hline
\end{tabular}
\end{center}
\end{table}

From Table \ref{table:refactorability}, we can see that 38.22\% of the clones can directly be refactored through method extraction (and possibly other refactoring techniques based on the relation of the clone instances). For the other clones, other techniques or transformations will be required.
